---
title: "Temperature Heat Map for cities in Malaysia"
author: "Low Cheng Kuan, John Law Leh Ping, Lee Joe Juan, See Kai Jun"
date: "12/19/2017"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(vioplot)
library(jsonlite)
library(shiny)
library(shinyjs)
library(curl)
library(data.table)
library(leaflet)
library(leaflet.extras)

```

## Objective

Capture and display Malaysia temperature / weather in heat map in real time.
<br>
<br>
Steps taken
<li> Obtain a list of coordinates for total of 220 cities in Malaysia (http://bulk.openweathermap.org/sample/city.list.json.gz)
<li> Query live data from openweathermap API (http://api.openweathermap.org/data/2.5/box/city)
<li> Extract temperature data for Malaysia Cities
<li> Render data into parameters and plot Leftlet map

## Data info
Data for cities in Malaysia
```{r, echo=FALSE}
cityListDF <- fromJSON("city.list.json.gz")
mycityListDF <- subset(cityListDF, cityListDF$country == 'MY')
```

```{r}
str(mycityListDF)
```

```{r}
minlon <- min(mycityListDF$coord$lon) - 1  
maxlon <- max(mycityListDF$coord$lon) + 1
minlat <- min(mycityListDF$coord$lat) - 1
maxlat <- max(mycityListDF$coord$lat) + 1

boxWeatherInfoUtl <- paste0('http://api.openweathermap.org/data/2.5/box/city?bbox=',minlon,',',minlat,',',maxlon,',',maxlat,',','200','&appid=4e6c991cd69de992db2a57796bee4bc9', sep='')
allWeatherInfo <- fromJSON(boxWeatherInfoUtl)

id = allWeatherInfo$list$id
temp = allWeatherInfo$list$main$temp
resultWeather <- data.frame(id, temp)

latestCityTemp <- merge( mycityListDF, resultWeather, by=c("id"))

```

## Weather Data

```{r}
str(latestCityTemp)
```

## The find out of data

violin plot displays density and distribution of temperatures

```{r, echo=FALSE, fig.width=8, fig.heighth=10}
vioplot(latestCityTemp$temp, col=rgb(0.1,0.4,0.7,0.7), names="temperature", horizontal=TRUE )
```

## Top 5 Hotest and Coldest Cities in Malaysia

```{r, echo=FALSE}
head(latestCityTemp[order(latestCityTemp$temp,decreasing=TRUE),c("name","temp")],n=5)
tail(latestCityTemp[order(latestCityTemp$temp,decreasing=TRUE),c("name","temp")],n=5)
 
```

## Interactive Plot

```{r eruptions}

plotMap <- function(input, output){
  
  # Querying live data from openweathermap API
  # Example url:
  # http://api.openweathermap.org/data/2.5/box/city?bbox=99,0,120,10,10&appid=4e6c991cd69de992db2a57796bee4bc9
  # id = the id for querying service (4e6c991cd69de992db2a57796bee4bc9)
  boxWeatherInfoUtl <- paste0('http://api.openweathermap.org/data/2.5/box/city?bbox=',minlon,',',minlat,',',maxlon,',',maxlat,',','200','&appid=4e6c991cd69de992db2a57796bee4bc9', sep='')
  allWeatherInfo <- fromJSON(boxWeatherInfoUtl)
  
  # Extract the data from the responded data to fit into Leftlet map ploting parameters
  # 
  id = allWeatherInfo$list$id
  temp = allWeatherInfo$list$main$temp
  resultWeather <- data.frame(id, temp)
  
  # Only select the cities in Malaysia
  latestCityTemp <- merge( mycityListDF, resultWeather, by=c("id"))
  
  #Extract the lists required for map plotting
  lon.list <- latestCityTemp$coord$lon  # longitude list
  lat.list <- latestCityTemp$coord$lat  # longitude list
  temp.list <- latestCityTemp$temp      # temperature list
  
  #Popup marker
  popup.list <- paste0(latestCityTemp$name, ', ', latestCityTemp$temp, intToUtf8(176), 'C')
  
  # Rendering the leftlet map plotting
  output$mymap <- renderLeaflet({
    
    leaflet() %>%
      addTiles() %>%
      #addMarkers(lng=lon.list, lat=lat.list,  popup=popup.list, label = popup.list ) %>%
      addHeatmap(lng=lon.list, lat=lat.list, minOpacity = input$opacity[1], max = input$opacity[2], blur = input$blur, intensity = (temp.list), gradient = c('yellow','red'), radius = input$radian)%>%
      addCircleMarkers( radius = 6, color = 'red', stroke = FALSE, fillOpacity = 0.5, lng=lon.list, lat=lat.list,  popup=popup.list, label = popup.list)
  })
}

pageWithSidebar(
  headerPanel("Temperature HeatMap for cities in Malaysia"),
  sidebarPanel(
    actionButton("do", "Reload"),
  sliderInput("opacity", "Opacity",
              min = -50., max = 50., value = c(20, 40)),
  sliderInput("blur", "Blur", 
              min = 0, max = 100, value= 20),
  sliderInput("radian", "radian", 
              min = 0, max = 50, value= 20)
  ),
  mainPanel(
    # Use imageOutput to place the image on the page
    leafletOutput("mymap")
  )
)


inputPanel(
  #titlePanel("Temperature HeatMap for cities in Malaysia"),
  
)

renderPlot({
  plotMap(input, output)
  
  observeEvent(input$do, {
      # reload data
      plotMap(input, output)
  })
  
  observeEvent(input$opacity, {
    # reload data
    plotMap(input, output)
  })
  
  observeEvent(input$blur, {
    # reload data
    plotMap(input, output)
  })
  
  observeEvent(input$radian, {
    # reload data
    plotMap(input, output)
  })
})
```
